%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experiences}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Researcher} % Job title
  {St. Anthony Falls Laboratory, University of Minnesota} % Organisation
  {Minneapolis, MN} % Location
  {Nov 2021 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a hybrid framework combining quantum circuits with physics-informed neural networks (PINNs) to simulate incompressible turbulence.}   
      \item {Applied quantum tensor networks for data compression and acceleration in turbulence simulations.}
      \item {Adapted and maintained in-house Fortran code for multi-GPU parallel computing using C++, CUDA, and CUDA-aware MPI.}
      \item {Developed a variational quantum algorithm to solve the Poisson equation.}
      \item {Investigated oil-wind-wave interactions, creating a CFD algorithm for three-phase interface capture and analyzing turbulence in bubble-oil-wave interactions.}
    \end{cvitems}
  }



\cventry
  {Postdoctoral Associate} % Job title
  {St. Anthony Falls Laboratory, University of Minnesota} % Organisation
  {Minneapolis, MN} % Location
  {Sep 2018 - Nov 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a novel method to simulate two-phase incompressible flows at high-density ratio and high Reynolds number, enhancing robustness.}
      \item {Researched wind-wave-bathymetry interactions near the surf zone to optimize amphibious vehicle performance, improving in-house code for interface tracking and fluid-structure interaction.}
      \item {Simulated indoor airflow and aerosol transport to study COVID-19 transmission mechanisms.}
      \item {Optimized hydro-turbine geometries using immersed boundary methods, supporting erosion protection and energy extraction from turbulence in hydropower installations.}
    \end{cvitems}
  }


%     Simulation-based study of hydropower: Conducted simulation-based study on the flow past hydro-turbines;
% optimized the geometries of turbines under different flow conditions; the findings led to a patent (US Patent No.
% 10502178) for a vertical-axis hydro-power system; published results in Renewable Energy.
% ◦ Development of a technique for tracking bubbles and detecting fragmentation and coalescence:
% Proposed a robust and accurate algorithm for Lagrangian tracking of bubbles and detecting fragmentation and
% coalescence, which is called Optimal Network (ON) methods; published results in International Journal of
% Multiphase Flow ; See an introductory animation through this link .




\cventry
  {Visiting Scholar} % Job title
  {University of Minnesota} % Organisation
  {Minneapolis, MN} % Location
  {Sep 2015 - Sep 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed in-house code for simulating multiphase turbulent flow, incorporating VOF, level set methods for two-phase interfaces, and immersed boundary method for solid objects.}
      \item {Researched turbulent cavitating flows interacting with ocean waves.}
    \end{cvitems}
  }

\cventry
  {Research Assistant} % Job title
  {Peking University} % Organisation
  {Beijing} % Location
  {Sep 2012 - Jul 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed in-house code to simulate compressible multiphase turbulence.}
      \item {Researched particle preferential concentration in compressible turbulent flows, focusing on clustering, dispersion, and concentration under shock wave effects.}
      \item {Investigated Richtmeyer-Meshkov Instability and turbulent mixing, modeling the energy transfer process during turbulent mixing process.}
    \end{cvitems}
  }


    

\end{cventries}
