%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {St. Anthony Falls Laboratory, University of Minnesota} % Organisation
    {Quantum-Inspired Computing for Fluid Mechanics} % Project
    {Minneapolis, MN} % Location
    {2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Developing tensor network methods for solving Navier-Stokes equations with potential exponential speedup.}
        \item {Encoding velocities and pressure as matrix product states (MPS) and implementing finite differences via matrix product operators (MPO).}
        \item {Proposed tensor networks-based level set method for tracking phase interfaces in multiphase flows.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {St. Anthony Falls Laboratory, University of Minnesota} % Organisation
    {Multiphase Flow Simulation} % Project
    {Minneapolis, MN} % Location
    {2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {High-fidelity simulation of ventilated cavitation, air-water-oil interface dynamics, and bubble tracking.}
        \item {Developed coupled level set and volume of fluid methods for two-phase flows at high density ratios and Reynolds numbers.}
        \item {Applied to practical problems including oil spill dynamics in breaking waves and amphibious vehicle hydrodynamics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {St. Anthony Falls Laboratory, University of Minnesota} % Organisation
    {COVID-19 Airborne Transmission Simulation} % Project
    {Minneapolis, MN} % Location
    {2020 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Simulated indoor airflow and aerosol transport to study COVID-19 transmission mechanisms in practical settings.}
        \item {Published as Featured Article in Physics of Fluids; featured in The Guardian.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
